 % Load the kaobook class
\documentclass[
	fontsize=10pt, % Base font size
	twoside=false, % Use different layouts for even and odd pages (in particular, if twoside=true, the margin column will be always on the outside)
	%open=any, % If twoside=true, uncomment this to force new chapters to start on any page, not only on right (odd) pages
	secnumdepth=1, % How deep to number headings. Defaults to 1 (sections)
]{kaobook}

\usepackage[english]{babel} % Load characters and hyphenation
\usepackage[english=british]{csquotes}	% English quotes
\usepackage{kaobiblio}
%\addbibresource{minimal.bib}
\usepackage{kaotheorems}

% Load the package for hyperreferences
\usepackage{kaorefs}

\graphicspath{{images/}{./}} % Paths where images are looked for

\makeindex[columns=3, title=Alphabetical Index, intoc]
\begin{document}

%----------------------------------------------------------------------------------------
%	BOOK INFORMATION
%----------------------------------------------------------------------------------------

\titlehead{A manual for MA2007B}
\title[Applications of Geometry and Topology for Data Science]{Applications of Geometry and Topology for Data Science}
\author[AUP]{Alejandro Ucan-Puc}
\date{\today}
\publishers{Instituto Tecnólogico y de Estudios Superiores de Monterrey}

\maketitle
%----------------------------------------------------------------------------------------

\frontmatter % Denotes the start of the pre-document content, uses roman numerals
%----------------------------------------------------------------------------------------
%	PREFACE
%----------------------------------------------------------------------------------------

%\chapter*{Preface}


%----------------------------------------------------------------------------------------
%	TABLE OF CONTENTS & LIST OF FIGURES/TABLES
%----------------------------------------------------------------------------------------

\begingroup % Local scope for the following commands

% Define the style for the TOC, LOF, and LOT
%\setstretch{1} % Uncomment to modify line spacing in the ToC
%\hypersetup{linkcolor=blue} % Uncomment to set the colour of links in the ToC
\setlength{\textheight}{230\vscale} % Manually adjust the height of the ToC pages

% Turn on compatibility mode for the etoc package
\etocstandarddisplaystyle % "toc display" as if etoc was not loaded
\etocstandardlines % "toc lines as if etoc was not loaded

\tableofcontents % Output the table of contents

\listoffigures % Output the list of figures

% Comment both of the following lines to have the LOF and the LOT on different pages
\let\cleardoublepage\bigskip
\let\clearpage\bigskip

\listoftables % Output the list of tables

\endgroup

%----------------------------------------------------------------------------------------
%	MAIN BODY
%----------------------------------------------------------------------------------------

\mainmatter % Denotes the start of the main document content, resets page numbering and uses arabic numbers
\setchapterstyle{kao} % Choose the default chapter heading style

\chapter{Introduction to Topology}

%\pagelayout{wide} % No margins
%\addpart{aasja}
%\pagelayout{margin} % Restore margins

Topology was first studied in...

\section{Basic concepts and Examples}

Topology is the study of properties that are preserved under continuous functions in a generic way, for this reason, we need to work with objects that are proper to the space and these objects are subsets. The set theory is needed to properly understand topology because it is the main language of the theory, if you need a refresh of set theory you can see the reference.

\begin{definition}[Topological Space]
Let $X$ be a set and $\tau$ a collection of subsets of $X.$ We say that $\tau$ is a \emph{topology} for $X$ is it satisfies:
\begin{enumerate}
\item If the total and the empty set belong to $\tau.$  $$\varnothing, X\in\tau.$$

\item For every subcollection of elements of $\tau,$ let say $\{U_\alpha\}_{\alpha\in A},$ we have that its union is an element of $\tau.$ $$\bigcup_{\alpha \in U} U_\alpha \in \tau.$$

\item For every finite subcollection of elements of $\tau,$ let say $\{U_j\}_{j=1}^n,$ we have that its intersection is an element of $\tau.$ $$ \bigcap_{j=1}^n U_j\in\tau.$$
\end{enumerate}

The elements of $\tau$ are called \emph{open sets} of $X$ and the pair $(X,\tau)$ is called a \emph{topological space}.
\end{definition}

This is not the first time that we see the concept of openness, for example in calculus we already worked with open intervals, open boxes (the real plane or space), and open disks (complex numbers). Topology theory intends to generalize this concept to general sets.

\begin{example}[Trivial topology]
Let $X$ be any set and consider the collection $\tau=\{\varnothing, X\}.$ $\tau$ is a topology for $X$ and it is called the trivial topology. 

This is not the best topology to understand properties of $X$ but it is a good counterexample when you want to generalize topological constructions.
\end{example}

\begin{example}[Discrete topology]
Let $X$ be any set and consider the collection $2^X=\{\mbox{all possible subsets of } X\}.$ $\tau$ is a topology for $X$ and it is called the discrete topology. 

Note that each element of $X$ is an open set on this topology. 
\end{example}

\begin{example}[Co-finite topology]
Let $X$ be any set and consider the collection $\tau_{cf}=\{U\subset X: X\setminus U \mbox{ is finite}\},$ i.e., the complement of $U$ in $X$ is a finite set of points. $\tau$ is a topology for $X$ and it is called the co-finite topology. 
\end{example}


\begin{example}[Spaces with different topologies]
Let $X=\{1,3,5,7\}$ and consider the collections

\begin{eqnarray*}
\tau_1 &=& \{\varnothing, \{1\},\{5\},\{7\},\{1,5\},\{1,7\},\{5,7\},\{1,5,7\},X\}. \\
\tau_2 &=& \{\varnothing, \{1\},\{3\},\{7\},\{1,3\},\{1,7\},\{3,7\},\{1,3,7\},X\}.
\end{eqnarray*}

Both $(X,\tau_1)$ and $(X,\tau_2)$ are topological spaces but they are not the same space. For example, the open set $\{1,5\}$ is not part of $(X,\tau_2)$ and $\{1,3\}$  is not part of $(X,\tau_1).$ 

Therefore in order to obtain the same topological space we need to find exactly the same open sets in both topologies.
\end{example}


\chapter{Second Chapter}

\appendix % From here onwards, chapters are numbered with letters, as is the appendix convention

\pagelayout{wide} % No margins
\addpart{Appendix}
\pagelayout{margin} % Restore margins

\chapter{Some more blindtext}


%----------------------------------------------------------------------------------------

\end{document}